Personal Total Income of Individual in the United States of America in 2023

### 2024-10-25 paper/paper.qmd
Update data importing path & Modify the updated data in Model Section in Paper

Note that according to our previous analysis in @#sec-eda, the interaction term, `EDUC_SEX_INTERACTION`, was included to capture the combined effect of education level and gender on income. This allowed us to model the non-linear relationship between these two variables and their joint impact on the outcome variable.

@@

| Feature                     | Coefficient |
|-----------------------------|-------------|
| `cat__MORTGAGE`             | 9971.56     |
| `num__AGE`                  | 397.66      |
| `cat__STATEICP`             | 91.39       |
| `cat__IND1990`              | -44.49      |
| `cat__OCC2010`              | -201.61     |
| `num__EDUC_SEX_INTERACTION` | -2799.42    |
| `cat__MARST`                | -4929.08    |
| `cat__GQ`                   | -7172.27    |
| `cat__SCHLTYPE`             | -14947.02   |
:::

@@

| Feature                     | VIF      |
|-----------------------------|----------|
| cat\_\_STATEICP             | 3.874599 |
| cat\_\_GQ                   | 1.002446 |
| cat\_\_MORTGAGE             | 2.614057 |
| cat\_\_MARST                | 1.754080 |
| cat\_\_SCHLTYPE             | 1.242432 |
| cat\_\_OCC2010              | 2.953611 |
| cat\_\_IND1990              | 6.566724 |
| num\_\_AGE                  | 7.373021 |
| num\_\_EDUC_SEX_INTERACTION | 7.066118 |
:::

@@

| Metric                         | Value            |
|--------------------------------|------------------|
| Mean Squared Error (MSE)       | 7,178,302,129.51 |
| Root Mean Squared Error (RMSE) | 84,724.86        |
| R-squared                      | 0.11099          |
| Adjusted R-squared             | 0.11097          |
:::

>>>>

Note that according to our previous analysis in @sec-eda, the interaction term, `EDUC_SEX_INTERACTION`, was included to capture the combined effect of education level and gender on income. This allowed us to model the non-linear relationship between these two variables and their joint impact on the outcome variable.

@@

| Feature                     | Coefficient |
|-----------------------------|-------------|
| `cat__MORTGAGE`             | 11267.90    |
| `num__AGE`                  | 415.91      |
| `cat__STATEICP`             | 126.39      |
| `cat__IND1990`              | -43.18      |
| `cat__OCC2010`              | -139.55     |
| `num__EDUC_SEX_INTERACTION` | -1832.32    |
| `cat__MARST`                | -5541.39    |
| `cat__GQ`                   | -7956.89    |
| `cat__SCHLTYPE`             | -16320.74   |
:::

@@

| Feature                  | VIF       |
|--------------------------|-----------|
| cat__STATEICP            | 3.242254  |
| cat__GQ                  | 1.002419  |
| cat__MORTGAGE            | 2.658013  |
| cat__MARST               | 1.741158  |
| cat__SCHLTYPE            | 1.239412  |
| cat__OCC2010             | 3.187731  |
| cat__IND1990             | 8.490997  |
| num__AGE                 | 7.871046  |
| num__EDUC_SEX_INTERACTION| 6.945850  |
:::

@@

| Metric                     | Value              |
|----------------------------|--------------------|
| R-squared                  | 0.0774938018       |
| Adjusted R-squared         | 0.0774637241       |
| Mean Squared Error (MSE)   | 7,448,800,507.01   |
| Root Mean Squared Error (RMSE) | 86,306.43        |
:::
